My title

### 2024-03-12 paper/paper.qmd
updated model and cleaned data

# only includes 7 observations from hawaii
# Hawaii is historically a Democratic stronghold
```

@@

@@

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

>>>>

# only includes 7 observations from hawaii
# Hawaii is historically a Democratic stronghold
# only 4 samples from kansas
```

@@

```{r}
#| label: fig-electoral-map-survey
#| fig-cap: Electoral map based solely on the survey data
#| echo: false
library(ggplot2)
library(statebins)
survey_electoral_map <- survey_analysis_data %>% 
  group_by(state, vote_biden) %>% 
  summarise(n = n()) %>% 
  group_by(state) %>% 
  mutate(prop = n/sum(n)) %>% 
  filter(vote_biden == 1)

survey_electoral_map %>%
  mutate(statename = str_to_title(state)) %>%
  ggplot(aes(fill = prop, state = statename)) +
  geom_statebins() +
  scale_fill_gradient2(low = "#d12531", high = "#244999",
                       mid = "white", midpoint = mean(survey_electoral_map$prop)) +
  theme_classic() +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank()) +
  labs(fill = "Proportion Voting \nfor Biden",
       title = "Map of the US States that plan to support Joe Biden or Donald Trump")

# note extremely small sample sizes from Hawaii, Kansas, and Wyoming
# note that survey sample size was only 1000
```

@@
